Secure Multi-Party Computation with SCALE-MAMBA

### 2019-04-19 paper.tex
X

There are two main things done in the offline phase. The first one is the generation of a global MAC key $\alpha$. This MAC key is later used, to authentificate the different shares at the end of the computation. This key is also distributedly generated, i.e. only if all parties pool together their shares they can recover its value.\\

@@

For each multiplication operation in the online phase, we need one of the Beaver triples \( (\langle x_1 \rangle ,\langle y_1\rangle , \langle z_1\rangle )\) generated in the offline phase. In the offline phase we checked the quality of our triples, but we still allowed the possibility that each triple has an error \(e\) so that \(c=a*b+e\). To check the quality of our triple, we use a second triple \( (\langle x_2 \rangle ,\langle y_2\rangle ,\langle z_2\rangle )\) in a procedure called sacrificing it. Both triples are additively shared between all parties like the input values. In SPDZ both triples are completly unrelated to each other, and the sacrificing is done as follows:\\

Sacrificing of triples
Even though the triples are generated and each party holds the respective shares, there is still an allowed error \(e\) for each triple \( (\langle x_1 \rangle ,\langle y_1\rangle , \langle z_1\rangle )\) so that \(z_1=x_1*y_1+e\). To guarantee that the triples are really sound, the correctness has to be checked. This is done with a second triple \( (\langle x_2 \rangle ,\langle y_2\rangle ,\langle z_2\rangle )\) in a procedure called sacrificing, which uses the second triple to guarantee the soundness of the first. In SPDZ that is done as follows:\\
\begin{enumerate}
\item Choose a random variable \( r\) and open it to the other parties. This is done by each party generating a random share \(r_i\) and then calculating \(r=r_1+...+r_n\).
\item The parties calculate  \( p=r*\langle x_1 \rangle - \langle x_2 \rangle \) and \( \sigma=\langle y_1 \rangle -  \langle y_2 \rangle \) and partially open the results afterwards
\item The parties calculate \(\phi = r * \langle z_1 \rangle\ - \langle z_2 \rangle - \sigma * \langle x_2 \rangle - p * \langle y_2 \rangle - \sigma * p\) and then partially open the result
\item If \( \phi \) is 0 then the triples are correct and it is proceeded with \( (\langle x_1 \rangle ,\langle y_1\rangle , \langle z_1\rangle )\) as a correct, secretly shared and not revealed triple. Otherwise the system detected a malicious adversary and it aborts.\\
\end{enumerate}

Sacrificing of triples in SCALE-MAMBA

Comparison in Sacrificing
This small improvement in the protocol nearly halved the mathematical operations necessary for the creation of one beaver triple. This is huge, because the triple generation is one of the most time consuming task, so it sped up the offline phase. In following table, the differences between both sacrificing protocols can be seen:

@@

In the offline phase, ZPoKP are used to guarantee that the Beaver triples are calculated correctly, or atleast that they dont divert more than a specified error \(e\) the expected result.

@@

@@

\subsection{SPDZ 2.0 in medical healthcare}
In medical healthcare, preserving privacy plays a huge role because patient records hold highly sensitive data, thus, its a natural area for the application of privacy protecting techonologies.

@@

>>>>

There are two main things done in the offline phase. The first one is the generation of a global MAC key $\alpha$. This MAC key is later used, to authenticate the different shares at the end of the computation. This key is also distributively generated, i.e. only if all parties pool together their shares they can recover its value.\\

@@

For each multiplication operation in the online phase, we need one of the Beaver triples \( (\langle x_1 \rangle ,\langle y_1\rangle , \langle z_1\rangle )\) generated in the offline phase. In the offline phase we checked the quality of our triples, but we still allowed the possibility that each triple has an error \(e\) so that \(c=a*b+e\). To check the quality of our triple, we use a second triple \( (\langle x_2 \rangle ,\langle y_2\rangle ,\langle z_2\rangle )\) in a procedure called sacrificing it. Both triples are additively shared between all parties like the input values. In SPDZ both triples are completely unrelated to each other, and the sacrificing is done as follows:\\

GENERATION OF BEAVER TRIPLES

@@

In the offline phase, ZPoKP are used to guarantee that the Beaver triples are calculated correctly before the sacrificing, or atleast that they dont divert more than a specified error \(e\) from the expected result.

@@

\subsubsection{Sacrificing of triples}
Even though the triples are generated and each party holds the respective shares, there is still an allowed error \(e\) for each triple \( (\langle x_1 \rangle ,\langle y_1\rangle , \langle z_1\rangle )\) so that \(z_1=x_1*y_1+e\). To guarantee that the triples are really sound, the correctness has to be checked. This is done with a second triple \( (\langle x_2 \rangle ,\langle y_2\rangle ,\langle z_2\rangle )\) in a procedure called sacrificing, which uses the second triple to guarantee the soundness of the first. In SPDZ that is done as follows:\\
\begin{enumerate}
\item Choose a random variable \( r\) and open it to the other parties. This is done by each party generating a random share \(r_i\) and then calculating \(r=r_1+...+r_n\).
\item The parties calculate  \( p=r*\langle x_1 \rangle - \langle x_2 \rangle \) and \( \sigma=\langle y_1 \rangle -  \langle y_2 \rangle \) and partially open the results afterwards
\item The parties calculate \(\phi = r * \langle z_1 \rangle\ - \langle z_2 \rangle - \sigma * \langle x_2 \rangle - p * \langle y_2 \rangle - \sigma * p\) and then partially open the result
\item If \( \phi \) is 0 then the triples are correct and it is proceeded with \( (\langle x_1 \rangle ,\langle y_1\rangle , \langle z_1\rangle )\) as a correct, secretly shared and not revealed triple. Otherwise the system detected a malicious adversary and it aborts.\\
\end{enumerate}

\textbf{Sacrificing of triples in SCALE-MAMBA}

\textbf{Comparison of Sacrificing}
This small improvement in the protocol nearly halved the mathematical operations necessary for the scarification process. This is huge, because the triple generation is one of the most time consuming task, so it sped up the offline phase. In following table, the differences between both sacrificing protocols can be seen:

@@

\subsection{SPDZ 2.0 in medical healthcare}
In medical healthcare, preserving privacy plays a huge role because patient records hold highly sensitive data, thus, its a natural area for the application of privacy protecting technologies. In [TODO: REFERENCE] a clinical decision support system was implemented with SPDZ 2.0. The idea is that the system provides the optimal treatment for a patient with HIV based on the  records of similar patients in different hospitals. To preserve privacy, the hospitals compute the efficiency of one treatment for one patient together with SMPC.\\
The researchers used a setup of 20.000 patient records split between the hospitals, and were able to compute the effectiveness of 100 treatments for one patient in 24 minutes in the online phase. For calculating the effectiveness of one treatment, their algorithm needed 40 million multiplications. They only implemented the online phase of SPDZ, but showed that it scaled linearly with the amount of patient records.

TODO: CHECK HOW MANY HOSPITALS

Supposedly, the offline phase took them around 22 minutes.

@@

https://www.moodle.ch/lms/pluginfile.php/6253/mod\_book/chapter/25/mpc-book.pdf
